My title

### 2024-02-09 outputs/paper/paper.qmd
cleaning update: made 'in-person' consistent in all files

library(tidyverse)
library(palmerpenguins)
```

@@

ggplot(penguins, aes(x = island, fill = species)) +
  geom_bar(alpha = 0.8) +
  scale_fill_manual(values = c("darkorange","purple","cyan4"),
                    guide = "none") +
  theme_minimal() +
  facet_wrap(~species, ncol = 1) +
  coord_flip()
```

>>>>

library(tidyverse) # a collection of data-related packages
library(knitr) # for kable
library(kableExtra)
library(here)
library(ggbeeswarm)

#reading cleaned data
rhode = read_csv(
  file = here("outputs/data/cleaned_learningmodel/rhode.csv"),       
  show_col_types = FALSE
)

colorado = read_csv(
  file = here("outputs/data/cleaned_learningmodel/colorado.csv"),       
  show_col_types = FALSE
)

connecticut = read_csv(
  file = here("outputs/data/cleaned_learningmodel/connecticut.csv"),       
  show_col_types = FALSE
)

massachusets = read_csv(
  file = here("outputs/data/cleaned_learningmodel/massachusets.csv"),       
  show_col_types = FALSE
)
minnesota = read_csv(
  file = here("outputs/data/cleaned_learningmodel/minnesota.csv"),       
  show_col_types = FALSE
)

mississippi = read_csv(
  file = here("outputs/data/cleaned_learningmodel/mississippi.csv"),       
  show_col_types = FALSE
)

ohio = read_csv(
  file = here("outputs/data/cleaned_learningmodel/ohio.csv"),       
  show_col_types = FALSE
)
virginia = read_csv(
  file = here("outputs/data/cleaned_learningmodel/virginia.csv"),       
  show_col_types = FALSE
)
westvirginia = read_csv(
  file = here("outputs/data/cleaned_learningmodel/westvirginia.csv"),       
  show_col_types = FALSE
)
winscosin = read_csv(
  file = here("outputs/data/cleaned_learningmodel/winscosin.csv"),       
  show_col_types = FALSE
)

wyoming = read_csv(
  file = here("outputs/data/cleaned_learningmodel/wyoming.csv"),       
  show_col_types = FALSE
)

@@

library(dplyr)

# Assuming each state data frame has the same structure and columns
all_states <- bind_rows(
  colorado %>% mutate(state = "Colarado"),
  connecticut %>% mutate(state = "Connecticut"),
  massachusets %>% mutate(state = "Massachusets"),
  minnesota %>% mutate(state = "Minnesota"),
  mississippi %>% mutate(state = "Mississsippi"),
  ohio %>% mutate(state = "Ohio"),
  rhode %>% mutate(state = "Rhode Islands"),
  virginia %>% mutate(state = "Virginia"),
  westvirginia %>% mutate(state = "West Virginia"),
  winscosin %>% mutate(state = "Winscosin"),
  wyoming %>% mutate(state = "Wyoming"),

)

all_states$time_period_start <- as.Date(all_states$time_period_start, format = "%Y-%m-%d")
all_states$learning_model <- as.factor(all_states$learning_model)

library(ggplot2)

ggplot(all_states, aes(x = time_period_start, y = learning_model, color = state)) +
  geom_line() +
  labs(title = "Comparison of Learning Models in US States Over Time",
       x = "Time Period Start", y = "Learning Model") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
